---
title: "Introduction to the Tidyverse"
author: "Alejandro Gil-Gomez"
date: "4/24/2020"
output: github_document
---
## Overview from tidyverse website
The tidyverse is a set of packages that work in harmony because they share common data representations and API design. The tidyverse package is designed to make it easy to install and load core packages from the tidyverse in a single command.

If you’d like to learn how to use the tidyverse effectively, the best place to start is [R for data science](https://r4ds.had.co.nz/).

## Usage
library(tidyverse) will load the core tidyverse packages:

+ **ggplot2**, for data visualisation.
+ **dplyr**, for data manipulation.
+ **tidyr**, for data tidying.
+ **readr**, for data import.
+ **purrr**, for functional programming.
+ **tibble**, for tibbles, a modern re-imagining of data frames.
+ **stringr**, for strings.
+ **forcats**, for factors.

## Packages
As well as the core tidyverse, installing this package also installs a selection of other packages that you’re likely to use frequently, but probably not in every analysis. This includes packages for:

- Working with specific types of vectors:

    + **hms**, for times.
    + **lubridate**, for date/times.

- Importing other types of data:
    + **feather**, for sharing with Python and other languages.
    + **haven**, for SPSS, SAS and Stata files.
    + **httr**, for web apis.
    + **jsonlite** for JSON.
    + **readxl**, for .xls and .xlsx files.
    + **rvest**, for web scraping.
xml2, for XML.

- Modelling

    + **modelr**, for modelling within a pipeline
    + **broom**, for turning models into tidy data
    
    
## The packages I use the most are:

+ dplyr
+ readr
+ tidyr
+ ggplot2
+ purrr
+ broom

### Let's take a look

```{r setup}
knitr::opts_knit$set(root.dir = 'C:/Users/alexg/Google Drive/05-Proyectos/restlab_workshop/02-AlejandroGil-Tidyverse/')

#If you want to convert this Rmarkdown document into an R script. Run the following.
#knitr::purl("pathtofile/file.Rmd",documentation=2)

#Or setwd() 
#setwd('C:/Users/alexg/Google Drive/05-Proyectos/restlab_workshop/02-AlejandroGil-Tidyverse/')
```

```{r}
#Install the tidyverse if you haven't already.
#install.packages("tidyverse")
library(tidyverse)
```

### Readr
Readr is a package that allow us to load data into R. It is very similar to function you probably use already such as read_csv(). The main difference is that it can collect info from the type of the data in each column automatically.

Let's compare the two:
```{r}
#Base R
base_tab <- read.csv("data/iris.csv")
base_tab %>% head()
#readR
tidy_tab <- read_csv("data/iris.csv")
tidy_tab %>% head()
```

Readr supports these formats 

+ read_csv(): comma separated (CSV) files
+ read_tsv(): tab separated files
+ read_delim(): general delimited files
+ read_fwf(): fixed width files
+ read_table(): tabular files where columns are separated by white-space.
+ read_log(): web log files

It is faster than base R, and it lets you see errors during the importation.

**%>%**: The pipe operator connects tidyverse functions. Contrl+Shift+M

tidy_tab %>%
  head()

instead of

head(iris)


**tible**: This is the format of the dataframes the tidyverse uses:
```{r}
base_tab %>%
  class()

tidy_tab %>%
  class()
```

Learn more about [readr](https://readr.tidyverse.org/).

### Tidyr
This package is used for data tidying.

The most useful functions from this package are gather() and spread().

```{r}
#Take a loot at this data.frame. 
stocks <- data.frame(
  time = as.Date('2009-01-01') + 0:9,
  X = rnorm(10, 0, 1),
  Y = rnorm(10, 0, 2),
  Z = rnorm(10, 0, 4))
#Sometimes we need to organize the data in a different way in order to plot it or perform some analysis.
#Imagine we want to represent two variables called specification and value for columns 1:5 and represent it in a tidydata. We can use the function gather.
stock_narrow <- stocks %>%
  gather(stock, price, -time)

stock_narrow %>% 
  head()
#We can also do the opposite to gather, which is spread. This convert our narrow-data into wide date.
stock_wide <- stock_narrow %>%
  spread(stock, price)

stock_wide %>% 
  head()
```

There are other functions to tidy-up our data in this package, such as separate, this separate a column into multiple columns if they are separated by a character.
Learn more about [tidyr](https://tidyr.tidyverse.org/).

### Dplyr
This package is used for data manipulation. It contains several great functions. 

```{r}
mpg %>% 
  head()
```


These are the some of the most useful:

+ rename()
This is used to rename columns.
```{r}
mpg %>% 
  rename(company = manufacturer,
         cyllinders = cyl)
```


+ select()
This function selects a group of columns. You can also select by index.
```{r}
mpg %>% 
  select(model,year,trans)
```

+ filter()
```{r}
mpg %>% 
  filter(cyl>5, manufacturer=="audi")
```

+ mutate().
This calculates new columns from existing ones. Use transmute if you want only to keep the new calculated columns.
```{r}
mpg %>% 
  mutate(cty_hwy=cty*hwy)
```

+ count()
```{r}
mpg %>% 
  count(model)
```

+ arrange()
```{r}
mpg %>% 
  filter(manufacturer=="audi")%>% 
  arrange(cyl)
```

+ group_by() and summarise()
```{r}
mpg %>% 
  group_by(manufacturer,model) %>% 
  summarise(mean_cyl=mean(cyl),
            sd_cyl=sd(cyl))
```

Learn more about [dplyr](https://dplyr.tidyverse.org/).


## Broom
Broom is a package associated with the tidyverse that is used to summarize statistical models.

```{r}
library(broom)

mod <- lm(mpg ~ wt + qsec, data = mtcars)

mod
```

```{r}
tidy(mod)
```

```{r}
augment(mod)
```

```{r}
glance(mod)
```

Learn more about broom and how to combine it with dplyr [here](https://cran.r-project.org/web/packages/broom/vignettes/broom_and_dplyr.html)


### Ggplot2
Ggplot2 is used for data visualization. It is based in the grammar of graphics.
If you want to be a master of ggplot, you should watch the videos by Thomas Lin Pedersen.

[Intro To ggplot 2](https://www.youtube.com/watch?v=h29g21z0a68)
This video will show you the grammar of graphics and an introduction to ggplot2. The code below was used by Thomas Lin Pedersen in his online seminar.

## Introduction
We will look at the basic ggplot2 use using the faithful dataset, giving 
information on the eruption pattern of the Old Faithful geyser in Yellowstone
National Park.

```{r}
data("faithful")
# Basic scatterplot
ggplot(data = faithful, 
       mapping = aes(x = eruptions, y = waiting)) + 
  geom_point()
# Data and mapping can be given both as global (in ggplot()) or per layer
ggplot() + 
  geom_point(mapping = aes(x = eruptions, y = waiting),
             data = faithful)
```

If an aesthetic is linked to data it is put into `aes()`

```{r}
ggplot(faithful) + 
  geom_point(aes(x = eruptions, y = waiting, colour = eruptions < 3))
```

If you simple want to set it to a value, put it outside of `aes()`

```{r}
ggplot(faithful) + 
  geom_point(aes(x = eruptions, y = waiting),
             colour = 'steelblue')
```

Some geoms only need a single mapping and will calculate the rest for you

```{r}
ggplot(faithful) + 
  geom_histogram(aes(x = eruptions))
```

geoms are drawn in the order they are added. The point layer is thus drawn on
top of the density contours in the example below.

```{r}
ggplot(faithful, aes(x = eruptions, y = waiting)) + 
  geom_density_2d() + 
  geom_point()
```

### Stat
We will use the `mpg` dataset giving information about fuel economy on different 
car models.

Every geom has a stat. This is why new data (`count`) can appear when using 
`geom_bar()`.

```{r}
data("mpg")
ggplot(mpg) + 
  geom_bar(aes(x = class))
```

The stat can be overwritten. If we have precomputed count we don't want any 
additional computations to perform and we use the `identity` stat to leave the 
data alone

```{r}
mpg_counted <- mpg %>% 
  count(class, name = 'count')
ggplot(mpg_counted) + 
  geom_bar(aes(x = class, y = count), stat = 'identity')
```

Most obvious geom+stat combinations have a dedicated geom constructor. The one
above is available directly as `geom_col()`

```{r}
ggplot(mpg_counted) + 
  geom_col(aes(x = class, y = count))
```

Values calculated by the stat is available with the `after_stat()` function 
inside `aes()`. You can do all sorts of computations inside that.

```{r}
ggplot(mpg) + 
  geom_bar(aes(x = class, y = after_stat(100 * count / sum(count))))
```

Many stats provide multiple variations of the same calculation, and provides a
default (here, `density`)

```{r}
ggplot(mpg) + 
  geom_density(aes(x = hwy))
```

While the others must be used with the `after_stat()` function

```{r}
ggplot(mpg) + 
  geom_density(aes(x = hwy, y = after_stat(scaled)))
```

### Scales
Scales define how the mapping you specify inside `aes()` should happen. All 
mappings have an associated scale even if not specified.

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy, colour = class))
```

take control by adding one explicitly. All scales follow the same naming 
conventions.

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy, colour = class)) + 
  scale_colour_brewer(type = 'qual')
```

Positional mappings (x and y) also have associated scales.

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy)) + 
  scale_x_continuous(breaks = c(3, 5, 6)) + 
  scale_y_continuous(trans = 'log10')
```

### Facets
The facet defines how data is split among panels. The default facet 
(`facet_null()`) puts all the data in a single panel, while `facet_wrap()` and
`facet_grid()` allows you to specify different types of small multiples

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy)) + 
  facet_wrap(~ class)
```

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy)) + 
  facet_grid(year ~ drv)
```

### Coordinates
The coordinate system is the fabric you draw your layers on in the end. The 
default `coord_cartesion provides the standard rectangular x-y coordinate 
system. Changing the coordinate system can have dramatic effects
```{r}
ggplot(mpg) + 
  geom_bar(aes(x = class)) + 
  coord_polar()
```

```{r}
ggplot(mpg) + 
  geom_bar(aes(x = class)) + 
  coord_polar(theta = 'y') + 
  expand_limits(y = 70)
```

You can zoom both on the scale...

```{r}
ggplot(mpg) + 
  geom_bar(aes(x = class)) + 
  scale_y_continuous(limits = c(0, 40))
```

and in the coord. You usually want the latter as it avoids changing the plottet
data

```{r}
ggplot(mpg) + 
  geom_bar(aes(x = class)) + 
  coord_cartesian(ylim = c(0, 40))
```


Coordinate systems are particularly important in cartography. While we will not 
spend a lot of time with it in this workshop, spatial plotting is well supported
in ggplot2 with `geom_sf()` and `coord_sf()` (which interfaces with the sf 
package). The code below produces a world map. Try changing the `crs` argument 
in `coord_sf()` to be `'+proj=robin'` (This means using the Robinson projection). 

```{r}
# Get the borders of all countries
world <- sf::st_as_sf(maps::map('world', plot = FALSE, fill = TRUE))
world <- sf::st_wrap_dateline(world, 
                              options = c("WRAPDATELINE=YES", "DATELINEOFFSET=180"),
                              quiet = TRUE)
# Plot code
ggplot(world) + 
  geom_sf() + 
  coord_sf(crs = "+proj=moll")
```

Maps are a huge area in data visualisation and simply too big to cover in this 
workshop. If you want to explore further I advice you to explore the 
[r-spatial wbsite](https://www.r-spatial.org) as well as the website for the
[sf package](https://r-spatial.github.io/sf)

### Theme
Theming defines the feel and look of your final visualisation and is something
you will normally defer to the final polishing of the plot. It is very easy to 
change looks with a prebuild theme

```{r}
ggplot(mpg) + 
  geom_bar(aes(y = class)) + 
  facet_wrap(~year) + 
  theme_minimal()
```

Further adjustments can be done in the end to get exactly the look you want

```{r}
ggplot(mpg) + 
  geom_bar(aes(y = class)) + 
  facet_wrap(~year) + 
  labs(title = "Number of car models per class",
       caption = "source: http://fueleconomy.gov",
       x = NULL,
       y = NULL) +
  scale_x_continuous(expand = c(0, NA)) + 
  theme_minimal() + 
  theme(
    text = element_text('Avenir Next Condensed'),
    strip.text = element_text(face = 'bold', hjust = 0),
    plot.caption = element_text(face = 'italic'),
    panel.grid.major = element_line('white', size = 0.5),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.ontop = TRUE
  )
```

#### Exercises
Themes can be overwhelming, especially as you often try to optimise for beauty 
while you learn. To remove the last part of the equation, the exercise is to 
take the plot given below and make it as hideous as possible using the theme
function. Go absolutely crazy, but take note of the effect as you change 
different settings.

```{r}
ggplot(mpg) + 
  geom_bar(aes(y = class, fill = drv)) + 
  facet_wrap(~year) + 
  labs(title = "Number of car models per class",
       caption = "source: http://fueleconomy.gov",
       x = 'Number of cars',
       y = NULL)
```

Learn more about [ggplot2](https://ggplot2.tidyverse.org/)


## Extended ggplot

[Extended packages](https://www.youtube.com/watch?v=0m4yywqNPVY)
This video will show you other packages associated with ggplot


```{r, echo=FALSE}
packages <- c('ggrepel','patchwork',
  'ggraph','patchwork','gganimate',
  'gifski','ggrepel','ggforce','ggraph',
  'ggthemes','maps','sf','concaveman','remotes')
# Uncomment the next lines (remove the first #) to install the packages
# install.packages(packages)
# remotes::install_github("hrbrmstr/hrbrthemes")
```


### Plot composition
We start by creating 3 separate plots
```{r}
p1 <- ggplot(msleep) + 
  geom_boxplot(aes(x = sleep_total, y = vore, fill = vore))

p2 <- ggplot(msleep) + 
  geom_bar(aes(y = vore, fill = vore))

p3 <- ggplot(msleep) + 
  geom_point(aes(x = bodywt, y = sleep_total, colour = vore)) + 
  scale_x_log10()
```

Combining them with patchwork is a breeze using the different operators

```{r}
library(patchwork)
p1 + p2 + p3
(p1 | p2) / 
   p3
p_all <- (p1 | p2) / 
            p3
p_all + plot_layout(guides = 'collect')
p_all & theme(legend.position = 'none')
p_all <- p_all & theme(legend.position = 'none')
p_all + plot_annotation(
  title = 'Mammalian sleep patterns',
  tag_levels = 'A')
```


The `&` operator can be used with any type of ggplot2 object, not just themes.
Modify the code below so the two plots share the same y-axis (same limits)

```{r}
p1 <- ggplot(mtcars[mtcars$gear == 3,]) + 
  geom_point(aes(x = disp, y = mpg))
p2 <- ggplot(mtcars[mtcars$gear == 4,]) + 
  geom_point(aes(x = disp, y = mpg))
p1 + p2
```

Patchwork contains many features for fine tuning the layout and annotation. Very
complex layouts can be obtained by providing a design specification to the 
`design` argument in `plot_layout()`. The design can be defined as a textual 
representation of the cells. Use the layout given below. How should the textual 
representation be undertood.

```{r}
p1 <- ggplot(mtcars) + 
  geom_point(aes(x = disp, y = mpg))
p2 <- ggplot(mtcars) + 
  geom_bar(aes(x = factor(gear)))
p3 <- ggplot(mtcars) + 
  geom_boxplot(aes(x = factor(gear), y = mpg))
layout <- '
AA#
#BB
C##
'
p1 + p2 + p3 + plot_layout(design = layout)
```

### Animation
ggplot2 is usually focused on static plots, but gganimate extends the API and
grammar to describe animations. As such it feels like a very natural extension
of using ggplot2

```{r}
ggplot(economics) + 
  geom_line(aes(x = date, y = unemploy))
library(gganimate)
ggplot(economics) + 
  geom_line(aes(x = date, y = unemploy)) + 
  transition_reveal(along = date)
```

There are many different transitions that control how data is interpreted for
animation, as well as a range of other animation specific features

```{r}
ggplot(mpg) + 
  geom_bar(aes(x = factor(cyl)))
ggplot(mpg) + 
  geom_bar(aes(x = factor(cyl))) + 
  labs(title = 'Number of cars in {closest_state} by number of cylinders') + 
  transition_states(states = year) + 
  enter_grow() + 
  exit_fade()
```

#### Exercises
The animation below will animate between points showing cars with different 
cylinders.

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy)) + 
  ggtitle("Cars with {closest_state} cylinders") + 
  transition_states(factor(cyl))
```

gganimate uses the `group` aesthetic to match observations between states. By 
default the group aesthetic is set to the same value, so observations are 
matched by their position (first row of 4 cyl is matched to first row of 5 cyl 
etc.). This is clearly wrong here (why?). Add a mapping to the `group` aesthetic
to ensure that points do not move between the different states.

* * *

In the presence of discrete aesthetic mappings (`colour` below), the group is
deduced if not given. The default behaviour of objects that appear and disappear
during the animation is to simply pop in and out of existance. `enter_*()` and
`exit_*()` functions can be used to control this behaviour. Experiment with the
different enter and exit functions provided by gganimate below. What happens if 
you add multiple enter or exit functions to the same animation?

```{r}
ggplot(mpg) + 
  geom_point(aes(x = displ, y = hwy, colour = factor(cyl))) + 
  ggtitle("Cars with {closest_state} cylinders") + 
  transition_states(factor(cyl))
```

* * *

In the animation below (as in all the other animations) the changes happens at
constant speed. How values change during an animation is called easing and can
be controlled using the `ease_aes()` function. Read the documentation for 
`ease_aes()` and experiment with different easings in the animation.

```{r}
mpg2 <- tidyr::pivot_longer(mpg, c(cty,hwy))
ggplot(mpg2) + 
  geom_point(aes(x = displ, y = value)) + 
  ggtitle("{if (closest_state == 'cty') 'Efficiency in city' else 'Efficiency on highway'}") + 
  transition_states(name)
```

### Annotation
Text is a huge part of storytelling with your visualisation. Historically, 
textual annotations has not been the best part of ggplot2 but new extensions 
make up for that.

Standard geom_text will often result in overlaping labels
```{r}
ggplot(mtcars, aes(x = disp, y = mpg)) + 
  geom_point() + 
  geom_text(aes(label = row.names(mtcars)))
```

ggrepel takes care of that

```{r}
library(ggrepel)
ggplot(mtcars, aes(x = disp, y = mpg)) + 
  geom_point() + 
  geom_text_repel(aes(label = row.names(mtcars)))
```

If you want to highlight certain parts of your data and describe it, the 
`geom_mark_*()` family of geoms have your back

```{r}
library(ggforce)
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point() + 
  geom_mark_ellipse(aes(filter = gear == 4,
                        label = '4 gear cars',
                        description = 'Cars with fewer gears tend to both have higher yield and lower displacement'))
```

#### Exercises
ggrepel has a tonne of settings for controlling how text labels move. Often, 
though, the most effective is simply to not label everything. There are two
strategies for that: Either only use a subset of the data for the repel layer,
or setting the label to `""` for those you don't want to plot. Try both in the 
plot below where you only label 10 random points.

```{r}
mtcars2 <- mtcars
mtcars2$label <- rownames(mtcars2)
points_to_label <- sample(nrow(mtcars), 10)
ggplot(mtcars2, aes(x = disp, y = mpg)) + 
  geom_point() + 
  geom_text_repel(aes(label = label))
```

* * *

Explore the documentation for `geom_text_repel`. Find a way to ensure that the 
labels in the plot below only repels in the vertical direction

```{r}
mtcars2$label <- ""
mtcars2$label[1:10] <- rownames(mtcars2)[1:10]
ggplot(mtcars2, aes(x = disp, y = mpg)) + 
  geom_point() + 
  geom_text_repel(aes(label = label))
```

* * *

ggforce comes with 4 different types of mark geoms. Try them all out in the code
below:

```{r}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point() + 
  geom_mark_ellipse(aes(filter = gear == 4,
                        label = '4 gear cars'))
```

### Networks
ggplot2 has been focused on tabular data. Network data in any shape and form is
handled by ggraph

```{r}
library(ggraph)
library(tidygraph)
graph <- create_notable('zachary') %>% 
  mutate(clique = as.factor(group_infomap()))
ggraph(graph) + 
  geom_mark_hull(aes(x, y, fill = clique)) + 
  geom_edge_link() + 
  geom_node_point(size = 2)
```

dendrograms are just a specific type of network

```{r}
iris_clust <- hclust(dist(iris[, 1:4]))
ggraph(iris_clust) + 
  geom_edge_bend() + 
  geom_node_point(aes(filter = leaf))
```

#### Exercies
Most network plots are defined by a layout algorithm, which takes the network 
structure and calculate a position for each node. The layout algorithm is 
global and set in the `ggraph()`. The default `auto` layout will inspect the
network object and try to choose a sensible layout for it (e.g. dendrogram for a
hierarchical clustering as above). There is, however no optimal layout and it is
often a good idea to try out different layouts. Try out different layouts in the
graph below. See the [the website](https://ggraph.data-imaginist.com/reference/index.html)
for an overview of the different layouts.

```{r}
ggraph(graph) + 
  geom_edge_link() + 
  geom_node_point(aes(colour = clique), size = 3)
```

* * *

There are many different ways to draw edges. Try to use `geom_edge_parallel()` 
in the graph below to show the presence of multiple edges

```{r}
highschool_gr <- as_tbl_graph(highschool)
ggraph(highschool_gr) + 
  geom_edge_link() + 
  geom_node_point()
```

Faceting works in ggraph as it does in ggplot2, but you must choose to facet by
either nodes or edges. Modify the graph below to facet the edges by the `year` 
variable (using `facet_edges()`)

```{r}
ggraph(highschool_gr) + 
  geom_edge_fan() + 
  geom_node_point()
```

### Looks
Many people have already desgned beautiful (and horrible) themes for you. Use
them as a base

```{r}
p <- ggplot(mtcars, aes(mpg, wt)) +
  geom_point(aes(color = factor(carb))) +
  labs(
    x = 'Fuel efficiency (mpg)', 
    y = 'Weight (tons)',
    title = 'Seminal ggplot2 example',
    subtitle = 'A plot to show off different themes',
    caption = 'Source: It’s mtcars — everyone uses it'
  )
library(hrbrthemes)
p + 
  scale_colour_ipsum() + 
  theme_ipsum()
```

```{r}
library(ggthemes)
p + 
  scale_colour_excel() + 
  theme_excel()
```

## Drawing anything

```{r}
states <- c(
  'eaten', "eaten but said you didn\'t", 'cat took it', 'for tonight',
  'will decompose slowly'
)
pie <- data.frame(
  state = factor(states, levels = states),
  amount = c(4, 3, 1, 1.5, 6),
  stringsAsFactors = FALSE
)
ggplot(pie) + 
  geom_col(aes(x = 0, y = amount, fill = state))
```

```{r}
ggplot(pie) + 
  geom_col(aes(x = 0, y = amount, fill = state)) + 
  coord_polar(theta = 'y')
```

```{r}
ggplot(pie) + 
  geom_col(aes(x = 0, y = amount, fill = state)) + 
  coord_polar(theta = 'y') + 
  scale_fill_tableau(name = NULL,
                     guide = guide_legend(ncol = 2)) + 
  theme_void() + 
  theme(legend.position = 'top', 
        legend.justification = 'left')
```

```{r}
ggplot(pie) + 
  geom_arc_bar(aes(x0 = 0, y0 = 0, r0 = 0, r = 1, amount = amount, fill = state), stat = 'pie') + 
  coord_fixed()
```

```{r}
ggplot(pie) + 
  geom_arc_bar(aes(x0 = 0, y0 = 0, r0 = 0, r = 1, amount = amount, fill = state), stat = 'pie') + 
  coord_fixed() + 
  scale_fill_tableau(name = NULL,
                     guide = guide_legend(ncol = 2)) + 
  theme_void() + 
  theme(legend.position = 'top', 
        legend.justification = 'left')
```

```{r}
ggplot(mpg) + 
  # geom_bar(aes(x = hwy), stat = 'bin')
  geom_histogram(aes(x = hwy))
```

```{r}
ggplot(mpg) + 
  geom_bar(aes(x = hwy)) + 
  scale_x_binned(n.breaks = 30, guide = guide_axis(n.dodge = 2))
```



